Results

### 2018-11-14 Manuscript_draft/Manuscript_draft.Rmd
Changes

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016. A general overview of it is that reduces species fitness (REFS). Other general facts... Quantity of foreign pollen that arrives...

@@

>>>>

Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016. A general overview of it can reduce species fitness (REFS) but not in al the cases (Refs). Other general facts... Quantity of foreign pollen that arrives...

@@

Maybe another possible hypothesis to test is the reciprocity of the effect of heterospecifc pollen????

Use the sterile species as a proof of the mechanical interference. Was a mistake but seems cool proof!!!

### 2018-11-14 Manuscript_draft/Results.Rmd
Changes

```{r, echo=FALSE, message=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
#load environment
load("myEnvironment_mantel.RData")
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
#load environment
load("myEnvironment_mantel.RData")
```
